Self Regulation Ontology Retest Data Report

### 2018-02-17 code/SRO_Report.Rmd
updating report with new dataset

```{r}
hddm_refits %>%
  filter(adaptive_n_back.hddm_drift<0)
  # ggplot(aes(adaptive_n_back.EZ_drift))+
  # geom_histogram()

hddm_fullfits %>%
  filter(dv == "adaptive_n_back.hddm_drift" & value <0)
```

@@

TBD. Still need to figure out how to turn off the H.

One way to solve this would be to feed data in manually.

>>>>

@@

Plot flat estimates against

```{r}
retest_hddm_flat <- read.csv(paste0(retest_data_path, 'retest_hddm_flat.csv'))
retest_hddm_flat
```
